\documentclass[12pt]{article}
\begin{document}

\section{Introduction}

BattleFront is a war game, in which you command the brave and
honourable Red Pixel Army in its glorious struggle against the
vicious Empire of Blue. The object of the game is to capture all the
factories of the opposing side, thereby destroying their capacity to
resist and ending the war. 

\section{Build for Victory}

Your factories (and those of the hated enemy) produce reinforcements
for the front on a regular schedule. At the start of the game, these
reinforcements must march, on foot, to the front. This is slow, and
on the way they lose strength to disease, frostbite, and friendly-fire
accidents. Your task is to build railways to transport your pixels
efficiently. Rail travel is fast and attrition-less. Further, in the
press of war there is little time to train the officers of the RPA in
advanced strategy; left to themselves they simply march, as rapidly as
they can manage, to the sound of the guns. Railroads allow you to
direct where your reinforcements go, and thus achieve local
superiority in particular parts of the front. 

\section{Game controls}

Press `q' to quit, `p' to pause, `c' to toggle show-cooldown mode.

Select factories and depots by clicking on them. 

Control-click somewhere in your territory to order a new supply depot
built. If a depot is selected, a railroad connecting the two will also
be ordered. Both depots and railroads are initially incomplete;
reinforcements must be used to build them to usefulness. 

Click on a selected factory to change which outgoing railroad it sends
its reinforcements out on. If the railroad is incomplete, the
reinforcements will build it, section by section. 

Railroads initially have one locomotive; you can order more built by
selecting a depot at either end of the railroad, and control-clicking
on the other end. Locomotives cost one supply packet to build. Each
locomotive can carry one packet. 

When a packet reaches a depot (or is newly built in a factory), one of
four things will happen:
\begin{itemize}
\item If the depot is not complete, the packet will be used to build
  it. 
\item If the depot has an active outgoing railroad, and that railroad
  has a spare locomotive, the packet will be put on the railroad. 
\item If the depot is in accumulation mode, and has spare capacity,
  the packet will be stored in the depot. 
\item All else failing, the troops will be sent out to make their way
  to the front on foot. 
\end{itemize}


\end{document}
